External validation

### 2020-10-23 diagnostics/README.Rmd
Exclude RxRiskV

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, cache = TRUE)

@@

```{r}
names(ext_val_required_data)
```
Some of those are factor variables:
```{r}
ext_val_required_data %>% 
  select(where(is.factor)) %>% 
  pivot_longer(everything(), values_ptypes = list(value = character())) %>% 
  distinct() %>% 
  arrange(name, value) %>% 
  group_by(name) %>% 
  mutate(name = replace(name, duplicated(name), ""))
```
- `P_Sex` and `P_ASA` should be self-explanatory
- `P_BMI` is a broader categorization based on BMI and the [WHO classification] (https://www.euro.who.int/en/health-topics/disease-prevention/nutrition/a-healthy-lifestyle/body-mass-index-bmi) where overweight = "pre-obesity"  
- `P_DiaGrp` is based on ICD-10 codes recorded in SHAR and grouped into broader categories.

@@

```{r}
nms     <- names(ext_val_required_data)
comorbs <- nms[startsWith(nms, "c_")]
comorbs
```
... are logical/boolean indicators of comorbidities based on ICD-10/ATC codes from one year prior to THA, as recorded in our National Patient Register and medical prescription register. Individual codes were grouped according to Charlson and Elixhauser as codified by table 2 in @Quan2005, and as RxRisk V according to table 1 in @Pratt2018. Those conditions were then further combined according to table 1 in the drafted manuscript:

@@

We have the 90 day model from the shared R object;
```{r}
model <- fit_brl_reduced_lean$fit[[1]]
```

Let's assume we now have the `outcome` variable and a data frame `X` with the  predictors (I will use the Swedish data just as an example but this should of course be changed for the external validation).
```{r}
outcome <- df$outcome_infection_90d
X       <- ext_val_required_data
```

@@

Method 2 from table 1 in @Steyerberg2004.

@@

Method 3 from table 1 in @Steyerberg2004.

@@

The text output from `AUCci`, `AUCci2` and `AUCci3` should be enough. Hence, the same character string that gets printed above (but now stored in an object).
```{r}
AUCci_print  <- capture.output(AUCci)
AUCci2_print <- capture.output(AUCci2)
AUCci3_print <- capture.output(AUCci3)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

@@

```{r}
names(ext_val_required_data)
```

Some of those are factor variables:

```{r}
ext_val_required_data %>% 
  select(where(is.factor)) %>% 
  pivot_longer(everything(), values_ptypes = list(value = character())) %>% 
  distinct() %>% 
  arrange(name, value) %>% 
  group_by(name) %>% 
  mutate(name = replace(name, duplicated(name), ""))
```

-   `P_Sex` and `P_ASA` should be self-explanatory
-   `P_BMI` is a broader categorization based on BMI and the [WHO classification] (<https://www.euro.who.int/en/health-topics/disease-prevention/nutrition/a-healthy-lifestyle/body-mass-index-bmi>) where overweight = "pre-obesity"  
-   `P_DiaGrp` is based on ICD-10 codes recorded in SHAR and grouped into broader categories.

@@

```{r}
nms     <- names(ext_val_required_data)
comorbs <- nms[startsWith(nms, "c_")]
comorbs
```

... are logical/boolean indicators of comorbidities based on ICD-10/ATC codes from one year prior to THA, as recorded in our National Patient Register and medical prescription register. Individual codes were grouped according to Charlson and Elixhauser as codified by table 2 in \@Quan2005, and as RxRisk V according to table 1 in \@Pratt2018. Those conditions were then further combined according to table 1 in the drafted manuscript:

@@

We have the 90 day model from the shared R object;

```{r}
model <- fit_brl_reduced_lean$fit[[1]]
```

Let's assume we now have the `outcome` variable and a data frame `X` with the predictors (I will use the Swedish data just as an example but this should of course be changed for the external validation).

```{r}
outcome <- df$outcome_infection_90d
X       <- ext_val_required_data
```

@@

Method 2 from table 1 in \@Steyerbeg2004.

@@

Method 3 from table 1 in \@Steyerberg2004.

@@

The text output from `AUCci`, `AUCci2` and `AUCci3` should be enough. Hence, the same character string that gets printed above (but now stored in an object).

```{r}
AUCci_print  <- capture.output(AUCci)
AUCci2_print <- capture.output(AUCci2)
AUCci3_print <- capture.output(AUCci3)
```
